---
title: "Alexander Bates' CV"
author: Beatriz Milz
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: [ 'dd_cv.css', 'custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---
```{r metathis, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(glue)
library(icons)
library(scholar)
library(formattable)
library(ggplot2)
library(magrittr) # For the pipe
library(elmr) # The fly brain
source("cv_printing_functions.r")
```

<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- final academic icons -->

 
<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>

 
<!-- final font awesome -->

```{r, include=FALSE}
# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "",  
  pdf_mode = params$pdf_mode
)
CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

Aside
================================================================================

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://alexanderbates.github.io/resume/")
} else {
  plot3d(FAFB14, plotengine = "plotly")
}
```

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://alexanderbates.github.io/resume/")
} else {
  cat("<i class='fas fa-download'></i> [Download this resume in PDF](https://alexanderbates.github.io/asbates/resume/index.pdf).")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV$contact_info %>% glue_data("- <i class='fa fa-{icon}'></i> {contact}")
```

Software {#software}
--------------------------------------------------------------------------------

<i class="fas fa-box-open"></i> [Package {natverse}](https://natverse.github.io/natverse/) - Co-Author. 

Skills {#skills}
--------------------------------------------------------------------------------

```{r}
#print_skill_bars(CV)
ggplot(data=CV$skills, aes(x=skill, y=level)) +
  geom_bar(stat="identity", fill="#B32DB5")+
  theme_minimal()
```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](http://nickstrayer.me/datadrivencv/index.html).

Code available on <i class="fa fa-github"></i> [GitHub](https://github.com/alexanderbates/asbates). 

Last updated on `r Sys.Date()`. 

Main
================================================================================

Alexander Shakeel Bates {#title}
--------------------------------------------------------------------------------

```{r}
print_text_block(CV, 'intro')
```

```{r profile, echo = FALSE, warning=FALSE}
id <- "BOVTiXIAAAAJ&hl"
author <- scholar::get_profile(id)
df <- data.frame(total_cites = author$total_cites, h_index = author$h_index, i10_index = author$i10_index)
formattable(df, list(total_cites = color_bar("coral", fun = "normalize"), h_index = color_bar("lightgreen", fun = "proportion"), i10_index = color_bar("lightblue", fun = "proportion")))
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Research Projects {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_projects')
```

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```


Scientific Journals {data-icon=book }
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('publications')
```

Projects {data-icon=share-alt}
--------------------------------------------------------------------------------

::: aside

I'm an active participant in the local R community: I'm a co-organizer of R-Ladies São Paulo, and I have taught in several meetups and workshops, 
in the chapters São Paulo, Niterói, Curitiba and Goiânia.


I'm a co-organizer of [satRday São Paulo](https://saopaulo2019.satrdays.org/), [LatinR](https://latin-r.com/)  and [useR! 2021](https://user2021.r-project.org/). 

### Languages

**English:** native

**Spanish:** Beginner

### GRANTS

- <i class="far fa-star"></i> [LatinR 2019](https://latin-r.com/) - Travel and Conference.

- <i class="far fa-star"></i> [useR! 2019](https://user2019.r-project.org/). Diversity Scholarship - Travel and Conference.

- <i class="far fa-star"></i> [FAPESP Doctorate Scholarship](https://bv.fapesp.br/en/bolsas/185176/active-transparency-in-the-management-of-water-resources-in-the-sao-paulo-macrometropolis-using-the/)


### CONTACT

- <i class="fa fa-envelope"></i> beatriz.milz@usp.br

- <i class="fa fa-twitter"></i> [Twitter: `@`BeaMilz](https://twitter.com/BeaMilz)

- <i class="fa fa-github"></i> [GitHub: `@`beatrizmilz](https://github.com/beatrizmilz)

- <i class="fa fa-external-link-alt"></i> <a href='http://lattes.cnpq.br/5150665880581477'> Lattes </a> 

- <i class="fab fa-orcid"></i> <a href='https://orcid.org/0000-0002-3064-4486'> Orcid </a>  

- <i class="fa fa-home"></i> [beatrizmilz.com](https://beatrizmilz.com)

- <i class="fab fa-discourse"></i> [Discourse](https://discourse.curso-r.com/u/beatrizmilz/summary)

:::

```{r}
CV %<>% print_section('experience')
```

Selected Oral Communications {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('meetings')
```

:::aside

<i class="fas fa-download"></i> [Download](https://beatrizmilz.github.io/resume/index.pdf)
:::
